---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {
  font-family: "Monaco", Monospace;
  font-weight: normal;
  font-size: 15pt;
  
}

h2 {
  font-weight: bold;
  font-size : 30pt;
  
}
```

## What's going on with my sleep during Uni?

> **Import data:**

```{r}
# Read the CSV file
library(tidyverse)
logged_data <- read.csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTIE7VZPkZVKd8yY4K-8vxQhQVAVbyOA_pOH-zQqbe_HkOSwUQ_gaCpa-tKbUFYltaltpGOXCAaBltd/pub?gid=1735036210&single=true&output=csv")

# Rename variables

latest_data <- logged_data %>% 
  rename(Day = 2,
         Bedtime = 3,
         Duration = 4, 
         Energy_rating = 5, 
         Uni_Efficiency = 6,
         Caffein_intake = 7,
         Unsatistifaction_Cause = 8,
         Sleep_Satisfaction = 9,
         Anything_negativly_impacted = 11) 
```



> **Mapping out the change in sleep duration during the semester**

```{r}
latest_data %>% 
  ggplot() +
    geom_bar(aes(x = Duration, fill = Week.of.the.sememeter)) +
  labs(title = "Change in amount of sleep across the semester",
       x = "Duration of sleep (hours)",
       y = "Week")
```
From the chart, the Week 1 and week 2 had around 8 to 10 hours of sleep, wfrom week 3, we can see that sleep duration become less. 



> **Satisfaction changes as semester progresses**

```{r}
ggplot(data = latest_data) +
  geom_bar(aes(x = Week.of.the.sememeter, fill = Sleep_Satisfaction)) +
  labs(title = "Change in sleep satisfaction across the semester",
       x = "Week",
       y = "sleep satisfaction rating")

```
As we can see from the car chart, as semester progresses, we become more uncertain about the quality and time of our sleep. Which maybe be due to stress or workload. 



> **Summary value of Sleep duration**

```{r}
paste("The highest amount of sleep I had throughout the 4 weeks and 5 days of logging was",
      max(latest_data$Duration),
      "Hours.",
      "The lowest amount of sleep I had throughout the 4 weeks and 5 days of logging was",
      min(latest_data$Duration),
      "hours.", collapse = "")
paste("The mean amount spent in Cafe in the 4 weeks and 3 days of logging is",
      mean(latest_data$Duration),
      "hours.", collapse = "")
```

-   **Line plot showing changes weekly amount of sleep Averages**

```{r}
Avg_sleep_per_week <- latest_data %>%
  group_by(Week.of.the.sememeter) %>%
  summarise(avg_sleep = mean(Duration))

ggplot(Avg_sleep_per_week, aes(x = Week.of.the.sememeter, y = avg_sleep, group = 1)) +
  geom_line(color = "darkgreen") +
  geom_point(color = "red") +
  labs(title = "Average Sleep Duration Over the Weeks",
       x = "Week",
       y = "Average Sleep Duration (hours)") 
```
With this plot, it allows us to see overall change in sleeping habbits over the weeks of the semester. 



